---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# monitor50x30

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of monitor50x30 is to provide a user-friendly interface for performing regular survye monitoring actions:

- **Getting data.** Downloading survey microdata, combining it, and constructing a single set of data files.
- **Checking data completeness.** Generating a report on the progress of data collection and on whether all expected data for a PSU has been sent to the server.
- **Performing data quality checks.** Applying a set of validation rules, determining whether to reject/review each interview, and providing a tool to reject interviews with critical issues.

## Installation

Since monitor50x30 is not yet available on CRAN, it can be installed from GitHub as follows:

``` r
if (!require("pak")) install.packages("pak")
pak::pak("arthur-shaw/monitor50x30")
```

## Usage

To open the app's graphical interface, simply run this command in the R console:

```{r}
library(monitor50x30)
run_app()
```
